Incentivizing Exploration with Unbiased Subhistories

### 2018-11-02 llevel-overview.tex
editing...

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left(\sqrt{{1}/{T_1}}\right)$ and
$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the history of the entire first level, which provides
sufficiently accurate reward estimates for both arms.

@@

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
above does not get naturally resolved as in some of these boundary
cases---the ratios between the upper and lower bounds of $\Delta$ rise
from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
require more observations from level $(l-2)$ to distinguish two arms
at level $l$. The reason for this larger disparity is that, except the
first level, we can no longer guarantee sufficient number of pulls of
each arm. For example, as shown in Figure \ref{fig:llevel-connecting},
when we talk about having enough arm $a$ pulls in the history observed
by agents in $G_{l,1,1}$, it could be that only agents in group
$G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most
agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are
pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls
can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
ultimately makes the boundary cases harder to deal with.

We resolve this problem by introducing an additional type of \emph{amplifying groups}: $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left(\sqrt{{1}/({\log(T) T_1)}}\right)$ and
$O\left(\sqrt{{1}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the entire first-level history, which consists of
$\Omega(\log(T) T_1)$ pulls of each arm and provides sufficiently
accurate reward estimates to distinguish the two arms.

@@

In the $L$-level policy, such boundary cases occur for each
intermediate level $l\in \{2, \ldots, l-1\}$, but the issue mentioned
above does not get naturally resolved since the ratios between the
upper and lower bounds of $\Delta$ rise from $\Theta(\sqrt{\log(T)})$
to $\Theta(\log(T))$, and it would require more observations from
level $(l-2)$ to distinguish two arms at level $l$. The reason for
this larger disparity is that, except the first level, we can no
longer guarantee sufficient number of pulls of each arm. For example,
as shown in Figure \ref{fig:llevel-connecting}, when we talk about
having enough arm $a$ pulls in the history observed by agents in
$G_{l,1,1}$, it could be that only agents in group $G_{l-1,1,1}$ are
pulling arm $a$ and it also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This ultimately
makes the boundary cases harder to deal with.

We resolve this problem by introducing an additional type of \emph{amplifying groups}, called $\Gamma$-groups. For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels. When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm. 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
